A Data-Driven Framework for Neural Field Modeling

### 2011-01-12 ltx/first_order_framework/LaTeX_Manuscript.tex
changes to appendix A

\parham{(Reviewer1, Additional comments 2:) The preservation of the system's stability, identifiability, observability, and controllability properties is not guaranteed with the discretization. Observability is assumed and then verified with the estimation results. The stability of the discretized IDE is proven below. To do this, the model is written as the series
\begin{align}
	v_1(\mathbf{r}) &= \xi v_0(\mathbf{r}) + T_s g_0(\mathbf{r}) \\
	v_2(\mathbf{r})	&= \xi^2 v_0(\mathbf{r}) + T_s \left(\xi g_0(\mathbf{r}) + g_1(\mathbf{r}) \right) \\
	\vdots \, \, \, \, \, &= \, \, \, \, \, \vdots \nonumber \\
	v_{t+1}(\mathbf r) &= \xi^{t+1} v_0\left(\mathbf{r} \right) + T_s \sum_{i=0}^t \xi^i g_{t-i}(\mathbf{r}), \label{eq:fieldmodelseries}
\end{align}
where
\begin{equation}
	g_{t}(\mathbf{r}) = \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'}.
\end{equation}
Now, $g_t(\mathbf r)$ is always bounded since $0 \leq f(v_t(\mathbf r)) \leq 1$ and the area under the kernel is finite. To assess the stability of the discrete time system we assume that $g_t(\mathbf{r})$ is maximally saturated over the entire field for all time, which we denote as $g_{max}$. Substituting this into equation~\ref{eq:fieldmodelseries} yields
\begin{align}\label{vrecursiveinlimit}
	v_{t+1}(\mathbf r) &= \xi^{t+1}v_0(\mathbf r)+ g_{max} T_s \sum_{i=0}^t \xi^i \nonumber \\
	&=\xi^{t+1}v_0(\mathbf r) + \frac{ g_{max} T_s(1-\xi^{t+1})}{1-\xi}.
\end{align}
To study the asymptotic behaviour of the system we consider the limit as $t$ approaches infinity and in doing so we use a property of the geometric series to simplify equation \eqref{vrecursiveinlimit} to
\begin{equation}\label{simplifiedvrecursiveinlimit}
	v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)+\frac{g_{max} T_s}{1-\xi}.
\end{equation}
Substituting $\xi=1-\zeta T_s$ into equation \eqref{simplifiedvrecursiveinlimit} gives
\begin{equation}
	v_{t+1}(\mathbf r)=(1-\zeta T_s)^{t+1}v_0(\mathbf r)+\frac{g_{max}}{\zeta}.
\end{equation}
From this equation it can be seen that the system is stable if $0 < T_s < \tau$, where the synaptic time constant $\tau = 1/\zeta$. The sampling period was set to $T_s = 0.001 s$ and the time constant was set to $\tau = 0.01 s^{-1}$. Therefore, the discretization preserved the stability properties of the system.}

>>>>

\parham{(Reviewer1, Additional comments 2:) The preservation of the system's stability, identifiability, observability, and controllability properties is not guaranteed with the discretization. Observability is assumed and then verified with the estimation results. Here we show that if $0 < T_s < \tau$, where the synaptic time constant $\tau = 1/\zeta$,  the discretized IDE is stable. To do this, the model is written as the series
\begin{align}
	v_1(\mathbf{r}) &= \xi v_0(\mathbf{r}) + T_s g_0(\mathbf{r}) \\
	v_2(\mathbf{r})	&= \xi^2 v_0(\mathbf{r}) + T_s \left(\xi g_0(\mathbf{r}) + g_1(\mathbf{r}) \right) \\
	\vdots \, \, \, \, \, &= \, \, \, \, \, \vdots \nonumber \\
	v_{t+1}(\mathbf r) &= \xi^{t+1} v_0\left(\mathbf{r} \right) + T_s \sum_{i=0}^t \xi^i g_{t-i}(\mathbf{r}), \label{eq:fieldmodelseries}
\end{align}
where
\begin{equation}
	g_{t}(\mathbf{r}) = \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'}.
\end{equation}
Now, $g_t(\mathbf r)$ is always bounded since $0 \leq f(v_t(\mathbf r)) \leq 1$ and the area under the kernel is finite. To assess the stability of the discrete time system we assume that $g_t(\mathbf{r})$ is maximally saturated over the entire field for all time, which we denote as $g_{max}$. Substituting this into equation~\ref{eq:fieldmodelseries} yields
\begin{align}\label{vrecursiveinlimit}
	v_{t+1}(\mathbf r) &= \xi^{t+1}v_0(\mathbf r)+ g_{max} T_s \sum_{i=0}^t \xi^i \nonumber \\
	&=\xi^{t+1}v_0(\mathbf r) + \frac{ g_{max} T_s(1-\xi^{t+1})}{1-\xi}.
\end{align}
To study the asymptotic behaviour of the system we consider the limit as $t$ approaches infinity. Noting $0 < \xi <1$  we use a property of the geometric series to simplify equation \eqref{vrecursiveinlimit} to
\begin{equation}\label{simplifiedvrecursiveinlimit}
	v_{t+1}(\mathbf r)=\xi^{t+1}v_0(\mathbf r)+\frac{g_{max} T_s}{1-\xi}.
\end{equation}
Substituting $\xi=1-\zeta T_s$ into equation \eqref{simplifiedvrecursiveinlimit} gives
\begin{equation}
	v_{t+1}(\mathbf r)=(1-\zeta T_s)^{t+1}v_0(\mathbf r)+\frac{g_{max}}{\zeta}.
\end{equation}
From this equation it can be seen that if $0 < T_s < \tau$, the system is stable. The sampling period was set to $T_s = 0.001 s$ and the time constant was set to $\tau = 0.01 s^{-1}$. Therefore, the discretization preserved the stability properties of the system.}
